Notes on Wide Gap

### 2016-05-18 paper/wide_gap_notes.tex
still finding Pm=1E-2 critical params

The purely conducting boundary condition states that the axial component of the current ($\mathbf{J}_z = [\nabla \times \mathbf{B}]_z)$ must be zero at the walls. In the thin gap geometry, the purely conducting boundary condition on the azimuthal magnetic field is $\partial_x(B_y) = 0$ for axisymmetric perturbations. A spatially constant azimuthal field satisfies both the thin-gap MRI equations and this boundary condition. This neutral mode is formally included in the analysis of Umurhan et al 2007 and yields a second amplitude equation in the form of a simple diffusion equation. This amplitude equation decouples from the GLE because of the translational symmetry of the thin-gap geometry. Because that symmetry is not preserved in the wide-gap case, Umurhan et al postulate that slow variation in the wide-gap geometry will be governed by two coupled amplitude equations. However, the wide-gap conducting boundary condition $J_z = \frac{1}{r} \partial_r (r B_\phi) = 0$, together with the purely geometric term in Equation \ref{eq:By_perturbed}, conspire to prevent the wide-gap geometry from sustaining a neutral mode. We note that this mode would exist in a resistance-free approximation.

@@

The astrophysical magnetorotational instability operates in accretion disks and in stellar interiors. In accretion disks, differential rotation is imposed gravitationally by a central body. In a Taylor-Couette flow, differential rotation is created by rotating an inner cylinder faster than an outer cylinder. In a non ideal fluid

-- MRI mode can be conceptualized as a quantum mechanical particle in a box
-- In the ideal thin-gap case, V = constant, and thus invariant under parity. Walls and boundary conditions impose symmetric and antisymmetric states.
-- In the ideal wide-gap case, V is a function of r
-- I expect the coefficients of the GLE to be complex in the wide-gap case..

>>>>

The purely conducting boundary condition states that the axial component of the current ($\mathbf{J}_z = [\nabla \times \mathbf{B}]_z)$ must be zero at the walls. In the thin gap geometry, the purely conducting boundary condition on the azimuthal magnetic field is $\partial_x(B_y) = 0$ for axisymmetric perturbations. A spatially constant azimuthal field satisfies both the thin-gap MRI equations and this boundary condition. This neutral mode is formally included in the analysis of Umurhan et al 2007 and yields a second amplitude equation in the form of a simple diffusion equation. This amplitude equation decouples from the GLE because of the translational symmetry of the thin-gap geometry. Because that symmetry is not preserved in the wide-gap case, Umurhan et al postulate that slow variation in the wide-gap geometry will be governed by two coupled amplitude equations. However, the wide-gap conducting boundary condition $J_z = \frac{1}{r} \partial_r (r B_\phi) = 0$, together with the purely geometric term in Equation \ref{eq:By_perturbed}, conspire to prevent the wide-gap geometry from sustaining a neutral mode. We note that a neutral mode of the form $B_\phi(r) \propto \frac{1}{r}$ would exist in a resistance-free approximation.

@@

The astrophysical magnetorotational instability operates in accretion disks and in stellar interiors. In accretion disks, differential rotation is imposed gravitationally by a central body. In a Taylor-Couette flow, differential rotation is created by rotating an inner cylinder faster than an outer cylinder. For a non ideal fluid, the base flow (describe what's currently in section 1)...

-- MRI mode can be conceptualized as a quantum mechanical particle in a box

-- In the ideal thin-gap case, V = constant, and thus invariant under parity. Walls and boundary conditions impose symmetric and antisymmetric states.

-- In the ideal wide-gap case, V is a function of r

-- I expect the coefficients of the GLE to be complex in the wide-gap case..
